Validate Nash-Equilibrium Equilibrium Model in First-Price Reverse Auctions

### 2021-03-11 paper/paper.tex
update paper

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{apacite}
\usepackage{caption}
\usepackage{subcaption}

@@

\title{% 
    Validate Structural Analysis \\ 
    \large Testing GPV Method in First-Price Reverse Auctions}

@@

\section{Introduction}
% previous version  
% Auctions are a price-discovering mechanism in environments where there is no 
% well established known price for items. Participants at auctions have heterogenous
% valuations about the items being auctioned. The standard economic assumption is that 
% bidders draw independent or affalidated valuations before the auction starts and 
% submit their bids as a possibly 
% non-linear function of their valuations and preferences. At the end, winners 
% are determined according to certain rules. At the momement the winner is designated, 
% a particular objective of the auction mechanism that is employed is achieved, 
% such as social welfare maximization, revenue maximiaztion, etc.

@@

Participants at auctions submit bids for items based on their valuations and 
preferences of the items. There are many ways to think about the transformation from 
valuations and preferences into bids, and the usual economic approach is to consider 
the bids as a mathematical function of valuations and preferences, an approach which 
this paper will take. At the end of auctions, the winner(s) 
is designated based on certain auction rules and the auction data becomes available.
The data includes only bids, the final output of the bidding function, and the inputs, 
valuations and preferences, remain unknown. Yet interesting and useful analysis 
of auctions entails the knowledge about valuations and preferences. For example, 
to evaluate the performance of auctions, it is necessary to have access to bidder's 
valuations to determine if the particular mechanism has achieved its objective,
which leads to structural estimation.

Structural estimation assumes a particular model and uses statistical methods to 
estimate relevant parameters of the model. The calibrated model can then 
give predictions regarding objects that are being investigated. For example, 
in first-price sealed-bid reverse auctions, 
one of the mechanisms that the government uses for public project procurements, 
the simple assumption is that all participants independently draw costs from an 
identical cost distribution. 
Each bidder submits a sealed bid to the auctioneer and after all bidders have finished 
submission the winner is the one with the lowest bid. With this bidding model, 
structural estimation can be used 
to infer the cost distribution based on observed bids \cite{Guerreetal2000}.
Compared to regression analysis, structural estimation imposes a stringer set of 
assumptions on the data. But more than just discovering the correlation between 
variables as regression analysis does, structural estimation is able to produce stronger 
counter-factual predictions, such as the cost distribution as mentioned above.

The central assumption underlying structural estimation is that the model used 
is correct in a particular environment. To overcome such a drawback, alternative 
studies such as lab experiments are used to confirm the theory's validity. But 
laboratory environments ultimately differ from the real environments and 
the conclusions from laboratory studies may not hold in more realistic environments. 
The goal of this paper is to test model validity in a new different way by 
borrowing the techniques from statistical learning literature. In statistical 
learning, multiple models for predictive purposes are trained on part of the dataset 
and their performance is evaluated on another reserved split of 
the available dataset. The technique is called cross-validation 
and is used when there are candidate models and their performance needs to 
be compared to select the fittest one. In this paper, I will adapt the idea 
of cross-validation to test the predictiveness of economic models. By splitting 
data into training data and test data as in statistical learning, I will 
run structural estimation on the training data, simulate test data using the 
results from structural estimation, and compare the simulated data to actual 
test data. If the difference is statistically significant, that suggests 
unfitness of the model in the particular environment. 
In this paper, I will use data from government procurement auctions to test 
the first-price sealed-bid equilibrium model \cite{RileySamuelson1981} 
for structural estimation
\footnote{The original goal of this paper also includes comparing the cost 
distribution of DBE/MBE/WBE (standing respectively for Disadvantaged/Minority/Woman
Business Enterprise) to the cost distribution of other firms, which will add 
to the existing literature on understanding how DBE/MBE/WBE perform relative 
to other firms. But due to data availability on these types of firms 
and time constraints on the project as this is a 
term paper, this goal is omitted. }.

Similar work has been done in \citeauthor{ChernomazYushioto2019} 
\citeyear{ChernomazYushioto2019}, where they have compared the accuracy 
of semiparametric and nonparametric structural estimation methods in an 
asymmetric environment.

@@

For the model setup, suppose there are $n$ bidders in the auction, with 
$n \geq 2$, and 
there is a single, indivisible object being auctioned. Each bidder submits 
a sealed bid based on an observed cost before the auction. The 
bidder's cost $c$ is drawn i.i.d from a common distribution $F(\cdot)$ which is 
continuous with density $f(\cdot)$ on the support $[\underline{c}, \overline{c}] \subset \mathbb{R}^{+}$. 
All bidders are quasi-linear utility-maximizers, with the utility function 
$u(c, b) = b - c$. Bidders are therefore assumed to be risk-neutral. 
The number of bidders $n$, the cost distribution $F$ and its support are common 
knowledge to all bidders in the auction. Besides, each bidder $i$ can only observe her 
private cost $c_i$ and no one else's.

Different from first-price sealed-bid auctions where 
the highest bidder wins, in first-price sealed-bid reverse 
auctions the winner is the one who submits the 
lowest bid. In the following subsection, I will derive the 
Bayes-Nash Equilibrium in the FPSB reverse auction environment.
After I have characterized the equilibrium, now I will proceed to describe how 
private costs can be inferred from observed bids based on the equilibrium.

\subsection{Bayes-Nash Equilibrium}
For bidder $i$ in the auction, she needs to report a bid $b_i$ based on 
her private cost $c_i$. The bidder achieves maximal utility 
by maximizing the function 
$$ \max_{b_i} (b_i - c_i)P(\text{win}|b_i), $$ 
which is saying by picking an appropriate bid $b_i$, the bidder 
has a good balance between the revenue and probability of winning.

@@

The objective function therefore becomes 
$$ \max_{b_i} (b_i - c_i)[1-F(s^{-1}(b_i))]^{n-1}$$ 
and setting the derivative of it with respect to $b_i$ equal to 0 yields
\begin{align}
    [1-F(s^{-1}(b_i))]^{n-1} &= (b_i -c_i)(n-1)[1-F(s^{-1}(b_i))]^{n-2}f(s^{-1}(b_i))\frac{d s^{-1}(b_i)}{d b_i} \nonumber \\
    [1-F(c_i)]^{n-1} &= (s(c_i) -c_i)(n-1)[1-F(c_i)]^{n-2}f(c_i)\frac{1}{s'(c_i)} \nonumber \\
    1 &= (s(c_i)-v_i)(n-1)\frac{f(c_i)}{1-F(c_i)}\frac{1}{s'(c_i)}     \label{eqn:BiddingDiffQ}
\end{align}

@@

\subsection{Cost Inference}
Our interest, however, lies not in the particular solution 
of this differential equation, but in using it as an intermediate step 
in deriving cost as a function of bids, i.e. $s^{-1}(\cdot)$.

@@

\subsection{Estimation}
The estimation consists of two steps. In step 1, I recover costs $c$ based on 
observed bids $b$, by first non-parametrically estimating $G(b)$ and $g(b)$ 
and then using equation (\ref{eqn:ReverseFunction}) to 
generate pseudo-costs. In the second step, I can non-parametrically estimate the cost
density $f(c)$ from pseudo-costs.

The technique used to estimate $G(b)$ and $g(b)$, as well as $f(c)$, is called 
kernel density estimation and has the following form
\begin{equation}
    \hat{f}(x) = \frac{1}{nh}\sum_{i=1}^n K(\frac{x-x_i}{h}),
    \label{eqn:KDE_f}
\end{equation}
and 
\begin{equation}
    \hat{F}(x) = \frac{1}{n}\sum_{i=1}^n I(x_i \leq x), 
    \label{eqn:KDE_F}
\end{equation}
where I have a set of observables ${x_1, x_2, ... x_n}$. However, this  
kernel density estimation (\ref{eqn:KDE_f}) 
method suffers from boundary 
problem and instead, I will use the boundary-corrected kernel estimation 
method as proposed in \cite{HickmanHubbard2015}

This two-step estimation method has the advantage that to estimate cost 
distribution with observed bids, I do not need to assume a prior distribution 
of $f(c)$ to estimate it (which is a parametric method that works by 
first assuming the shape of a distribution and then estimating parameters of the 
distribution from data).

@@

\begin{figure}
\centering
    \begin{minipage}[h]{0.5\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{costDensity.jpg}
    \end{minipage}%
    \begin{minipage}[h]{0.5\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{costDistribution.jpg}
    \end{minipage}
\caption{Pseudocost density (on the left) and cost distribution (on the right)}
\label{fig:CostEstimation}
\end{figure}

@@

\section[title]{Simulation} 
To test if the estimated cost distribution captures the underlying cost 
distribution that induces observed bids, I will proceed to the validation stage: 
simulate bids using estimated cost distribution 
$F_c(\cdot)$ and comparing simulated bids to actual bids. For the test data, 
I will use an auction from the dataset which has 16 bidders. The data is not used 
to estimate the cost distribution because the total number of bids with 
$16$ bidders is less than $32$.

The simulation technique is known as the inversion method and runs as follows.
I will draw 16 random numbers uniformly 
distributed on the range $(0 ,1)$ and use the inverse distribution function, 
$F_c^{-1}(\cdot)$, to find the corresponding costs. The bids are then computed 
using equation (\ref{eqn:BiddingFunction}) and the estimated cost distribution 
$F_c$. This process is repeated 1000 times and the averages are taken.

@@

Figure \ref{fig:simulation} plots simulated costs against simulated bids that are 
inferred from simulated costs using equation (\ref{eqn:BiddingFunction}). 
The simulated costs and bids center around 110\% 
and the range is small, with the max and min differing by less than 4\%. This 
is due to the estimated unimodal cost distribution 
concentrating in the range [80, 200], with a peak around 110\%. 
With the inversion method repeated 1000 times, it is natural that 
the costs and bids fall into the place where most bids and costs are 
concentrated. With the number of runs curtailed to 100 and 50, as shown in 
Figure \ref{fig:simulation_run_times}, the bids become more spread out and 
closer to the bid distribution. This shows that the number of runs is 
an important factor to determine to have a more accurate simulation 
but it is outside the scope of this paper. For simplicity, I will keep 
referencing the data generated with 1000 runs.

@@

Figure \ref{fig:actualVsimulation} plots test data against simulated bids. 
A wide difference between simulation and test data is observed here. 
This difference, however, is not unexpected for two reasons: 
(1) the test data, which contains an auction with 16 bidders, does not conform 
to the bid distribution depicted in Figure \ref{fig:BidFrequency}, and 
(2) I am comparing most likely bids predicted by the estimated cost distribution 
to a particular auction. Therefore, the difference here does not suggest the 
inaccuracy of the estimated cost distribution or the equilibrium model. 
Instead, this exercise suggests that a larger test dataset is needed 
to deliver more informative results.

\section{Conclusion}
This paper tries to propose a way to validate models used in structural analysis 
by cross-validation. The dataset is split into training data and test 
data.
First, this paper conducts structural estimation on a government 
procurement auction dataset about highway constructions and estimates the 
cost distribution on the training data using a two-step nonparametric procedure.
Second, using the 
estimated cost distribution, the paper then constructs simulated bids with the 
inversion method and compare the simulation to test data. 
But the wide difference between the simulation and test data does not suggest
that the first-price sealed-bid equilibrium model introduced in 
\citeauthor{RileySamuelson1981} \citeyear{RileySamuelson1981}
is not a suitable model to predict bidder's 
behavior in real-world auctions. Instead, to draw a firm conclusion requires 
more data.

Moreover, in the second step of the cross-validation procedure, comparing bids 
directly to test theory's validity may not be a good idea, as suggested in 
\citeauthor{Harrison1989} \citeyear{Harrison1989}. \citeauthor{Harrison1989}
\citeyear{Harrison1989} instead proposes to "evaluate subject behavior in the 
expected payoff space", which can be incorporated into future work of the project.

The idea of cross-validation has been an old idea in the machine learning 
literature as a way to compare performance across models. I, therefore, consider 
it a natural idea to introduce it into structural analysis. Structural estimation 
relies on the model's correctness in modeling agent's behavior, but the verification 
of models is left to lab experiments, not empirical data which holds the final 
authority on models. Hopefully, this paper's experiment would shed light on 
possible directions that structural analysis can head to become more robust.

@@

>>>>

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{apacite}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[toc, page]{appendix}

@@

\title{% 
    Validate Nash-Equilibrium Equilibrium Model 
    in First-Price Reverse Auctions}

@@

\begin{abstract}
    This paper tests the predictive power of Bayes-Nash equilibrium model in 
    first-price procurement auctions through validation set approach. It 
    first trains the model on a subset of data using the Guerre-Perrigne-Vuong method 
    and then generates predictions on validation set using inversion method. 
    The generated predictions are compared to the actual data from validation set.
    This paper's result suggests that Bayes-Nash equilibrium model does not 
    yield accurate predictions but the answer might be more nuanced due to 
    flaws in the paper's approach. 
\end{abstract}

\section{Introduction}
% previous version  
% Auctions are a price-discovering mechanism in environments where there is no 
% well established known price for items. Participants at auctions have heterogenous
% valuations about the items being auctioned. The standard economic assumption is that 
% bidders draw independent or affiliated valuations before the auction starts and 
% submit their bids as a possibly 
% non-linear function of their valuations and preferences. At the end, winners 
% are determined according to certain rules. At the moment the winner is designated, 
% a particular objective of the auction mechanism that is employed is achieved, 
% such as social welfare maximization, revenue maximization, etc.

@@

Participants at auctions submit bids for items based on their valuations and 
preferences of the items. There are many ways to think about the transformation from 
valuations and preferences into bids, and one usual economic approach is to consider 
the bids as a (hopefully not complex) function of valuations and preferences,
an approach which this paper will take. At the end of auctions, the winner(s) 
is designated based on certain auction rules and the auction data becomes available.
The data includes only bids, the final output of the bidding function, whereas 
valuations and preferences remain unknown, both of which are inputs to the 
bidding function. Interesting and useful analysis 
of auctions would entail additional knowledge about valuations and preferences.
For example, 
to compare how well DBE (disadvantaged business enterprise) performs in government 
procurement relative to other types of business enterprises, besides looking 
at how much DBE firms bid in auctions, it would also be useful to compare 
project costs of DBE firms to those of others. As project costs are an unknown,
to do this essentially means conducting structural estimation on the data.

What is structural estimation? 
Structural estimation gives the ability to extract useful information from 
data, just like regression analysis. The difference lies in that structural 
analysis assumes a particular model and uses statistical methods to 
estimate relevant parameters of the model. The calibrated model can then 
generate predictions on objects of interest. For example, 
in first-price sealed-bid government procurement auctions, where 
the bidders who bids the lowest wins,
one way to do structural analysis is assuming that bidders draw their costs 
independently and use the same bidding function to make bids. 
By reverse engineering the bidding function, structural analysis 
can be used to infer the cost distribution from bids \cite{Guerreetal2000}. 
On the other hand, compared to regression analysis, 
structural estimation imposes a stronger set of 
assumptions on the data. These additional assumptions enable 
structural estimation to be able to produce 
counter-factual predictions that are not discoverable under 
regression analysis.

Yet assumptions structural estimation impose on data also come at a cost.
The central assumption underlying structural estimation is that the model used 
is correct in a particular environment of interest. 
But it is usually difficult to assess the model's fit in such environments. 
To overcome such a drawback, alternative 
studies such as lab experiments are used to confirm the theory's validity. 
Even though laboratory studies try to simulate real environments as much 
as possible, laboratory environments ultimately differ from those in real life 
and so the conclusions drawn from lab experiments do not necessarily hold true.

The goal of this paper is to test model validity in a new different way by 
borrowing techniques from statistical learning literature. In the 
prediction branch of statistical learning, a common 
technique to evaluate a model's performance is by training the model 
on a dedicated training set that is a subset of the available dataset and then 
tests the model's prediction on the validation set that is independent from the 
training set.  
In this paper, I will adapt the idea 
of validation set approach to investigate how well the equilibrium model 
performs in first-price procurement auctions. Specifically, I will 
split bidding data into training data and test data as in statistical learning.
Then I will 
run structural estimation on the training data, simulate test data using 
inversion method, and compare the simulated data to actual 
test data. If the difference is statistically insignificant, that suggests 
fitness of the model in the particular environment. 
Similar work has been done in \citeauthor{ChernomazYushioto2019} 
\citeyear{ChernomazYushioto2019}, where they have compared the accuracy 
of semiparametric and nonparametric structural estimation methods in an 
asymmetric environment.

In this paper, I will use data from government procurement auctions to test 
the first-price sealed-bid equilibrium model \cite{RileySamuelson1981} 
for structural estimation
\footnote{The original goal of this paper also includes comparing the cost 
distribution of DBE/MBE/WBE (standing respectively for Disadvantaged/Minority/Woman
Business Enterprise) to the cost distribution of other firms, which will add 
to the existing literature on understanding how DBE/MBE/WBE perform relative 
to other firms. But due to data availability on these types of firms 
and time constraints on the project as this is a 
term paper, this goal is omitted. }.

@@

For the model setup, suppose there are $n$ bidders in the auction, with 
$n \geq 2$, and 
there is a single, indivisible object being auctioned. Each bidder submits 
a sealed bid based on an observed cost before the auction. The 
bidder's cost $c$ is drawn i.i.d from a common distribution $F(\cdot)$ which is 
continuous with density $f(\cdot)$ on the support $[\underline{c}, \overline{c}] \subset \mathbb{R}^{+}$. 
All bidders are quasi-linear utility-maximizers, with the utility function 
$u(c, b) = b - c$. Bidders are therefore assumed to be risk-neutral. 
The number of bidders $n$, the cost distribution $F$ and its support are common 
knowledge to all bidders in the auction. Besides, each bidder $i$ can only observe her 
private cost $c_i$.

The paper focuses on the environment of first-price sealed-bid (FPSB) procurement 
auctions where the winner is the one who submits the 
lowest bid. In the following subsection, I will derive the 
Bayes-Nash Equilibrium in the FPSB reverse auction environment.
After I have characterized the equilibrium, I will proceed to describe how 
private costs can be inferred from observed bids with the assumption 
that players are following equilibrium strategy.

\subsection{Bayes-Nash Equilibrium}
For bidder $i$ in the procurement auction, she needs to report a bid $b_i$ based on 
her private cost $c_i$. The bidder achieves maximal utility 
by maximizing the function 
$$ \max_{b_i} (b_i - c_i)P(\text{win}|b_i), $$ 
which is saying by picking an appropriate bid $b_i$, the bidder 
has a good balance between the revenue ($b_i - c_i$) and probability of winning.

@@

The objective function therefore becomes 
$$ \max_{b_i} (b_i - c_i)[1-F(s^{-1}(b_i))]^{n-1}$$ 
and taking the first-order condition with respect to $b_i$ yields
\begin{align}
    [1-F(s^{-1}(b_i))]^{n-1} &= (b_i -c_i)(n-1)[1-F(s^{-1}(b_i))]^{n-2}f(s^{-1}(b_i))\frac{d s^{-1}(b_i)}{d b_i} \nonumber \\
    [1-F(c_i)]^{n-1} &= (s(c_i) -c_i)(n-1)[1-F(c_i)]^{n-2}f(c_i)\frac{1}{s'(c_i)} \nonumber \\
    1 &= (s(c_i)-v_i)(n-1)\frac{f(c_i)}{1-F(c_i)}\frac{1}{s'(c_i)}     \label{eqn:BiddingDiffQ}
\end{align}

@@

\subsection{Cost Inference}
Our interest, however, lies not in the particular solution 
of this differential equation, but in using it as an intermediate step 
to derive cost as a function of bids, $s^{-1}(\cdot)$.

@@

\subsection{Estimation}
The estimation consists of two steps. In step 1, I recover costs $c$ based on 
observed bids $b$, by non-parametrically estimating $G(b)$ and $g(b)$ 
and using equation (\ref{eqn:ReverseFunction}) to 
generate pseudo-costs. In step 2, I can then estimate the cost
density $f(c)$ from pseudo-costs.

The technique used to estimate $G(b)$ and $g(b)$, as well as $f(c)$, is called 
kernel density estimation and has the following form
\begin{equation}
    \hat{f}(x) = \frac{1}{nh}\sum_{i=1}^n K(\frac{x-x_i}{h}),
    \label{eqn:KDE_f}
\end{equation}
and 
\begin{equation}
    \hat{F}(x) = \frac{1}{n}\sum_{i=1}^n I(x_i \leq x), 
    \label{eqn:KDE_F}
\end{equation}
where ${x_1, x_2, ... x_n}$ are the set of observed values. However, this  
kernel density estimation (\ref{eqn:KDE_f}) 
method suffers from boundary 
problem: when the estimator is near the boundary values, the estimate 
will be downward biased. 
Instead, I will use the boundary-corrected kernel estimation 
method as proposed in \cite{HickmanHubbard2015}

This two-step non-parametric estimation method has the advantage that to estimate cost 
distribution from observed bids, I do not need to assume a prior distribution 
of $f(c)$, whereas a parametric method works by 
first assuming the shape of a distribution and then estimating parameters of the 
distribution from data. This helps avoid implications brought by assumed distributions.

@@

\begin{figure}
\centering
    \begin{minipage}[h]{0.5\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{costDensity.jpg}
    \end{minipage}%
    \begin{minipage}[h]{0.5\textwidth}
        \centering
        \includegraphics[width=1\linewidth]{costDistribution.jpg}
    \end{minipage}
\caption{Pseudo-cost density (on the left) and cost distribution (on the right)}
\label{fig:CostEstimation}
\end{figure}

@@

\section[title]{Simulation} 
To test if the estimated cost distribution captures the underlying cost 
distribution that induces observed bids, I will proceed to the validation stage: 
simulate bids using estimated cost distribution 
$F_c(\cdot)$ and comparing simulated bids to actual bids. 
The validation data comes form an auction with 16 bidders.

The simulation technique is known as the inversion method and runs as follows.
I will draw 16 random numbers uniformly 
distributed on the range $(0 ,1)$ and use the inverse distribution function, 
$F_c^{-1}(\cdot)$, to find the corresponding costs. The bids are then computed 
using equation (\ref{eqn:BiddingFunction}) and the estimated cost distribution 
$F_c$. This process is repeated 1000 times and the averages of each bid are taken.

@@

Figure \ref{fig:simulation} plots simulated costs against simulated bids that are 
inferred from simulated costs using equation (\ref{eqn:BiddingFunction}). 
The simulated costs and bids center around 110\% 
and the range is small, with the max and min differing by less than 4\%. This 
is due to the estimated unimodal cost distribution 
concentrating in the range [80, 200], with a peak around 110\%. 
With the inversion method repeated 1000 times, it is natural that 
the costs and bids fall into the place where most bids and costs are 
concentrated. With the number of runs curtailed to 100 and 50, as shown in 
Figure \ref{fig:simulation_run_times}, the bids become more spread out and 
closer to the bid distribution. This shows that the number of runs is 
an important factor to determine in order to have a more accurate simulation.
But determining the best number of runs is outside the scope of this paper.  
For the rest of this paper, I will keep 
referencing the data generated with 1000 runs.

@@

Figure \ref{fig:actualVsimulation} plots test data against simulated bids. 
A wide difference between simulation and test data is observed here. 
This difference, however, is not unexpected for two reasons: 
(1) the validation data, which contains an auction with 16 bidders, does not conform 
to the bid distribution depicted in Figure \ref{fig:BidFrequency}, and 
(2) I am comparing most likely bids predicted by the estimated cost distribution 
to a particular auction. Therefore, the difference here does not suggest the 
inaccuracy of the estimated cost distribution or the equilibrium model. 
Instead, this exercise suggests that a larger test dataset is needed 
to deliver more informative results and raises the need for a better 
way to compare simulation data to validation data.

\section{Conclusion}
This paper tries to propose a way to test economics models by validation set approach. 
It splits a government 
procurement auction dataset about highway constructions into training set and 
validation set. Then it estimates the 
cost distribution from training data assuming Bayes-Nash equilibrium model. 
Second, using the 
estimated cost distribution, it constructs simulated bids with the 
inversion method and compare the simulation to test data. 
Even though the wide difference between the simulation and test data suggests
that the first-price sealed-bid equilibrium model introduced in 
\citeauthor{RileySamuelson1981} \citeyear{RileySamuelson1981}
may be not an accurate model to predict bidder's 
behavior in such environment, the flaws in this paper's experiment design 
demand further investigation before any firm conclusion can be drawn. 
For example, 
in the second step of the cross-validation procedure, comparing bids 
directly to test theory's validity may not be a good idea, as suggested in 
\citeauthor{Harrison1989} \citeyear{Harrison1989}. \citeauthor{Harrison1989}
\citeyear{Harrison1989} instead proposes to "evaluate subject behavior in the 
expected payoff space", which can be incorporated into future work of the project.

The practice of using validation set to verify model's performance
has been standard in the statistical learning 
literature. I consider 
it a natural extension to introduce it into the economics field as a way to 
test how models match reality. As Structural estimation 
relies on the model's correctly modeling agent's behavior,
I hope the introduction of validation set approach would help with model 
verification besides lab experiments and would help structural estimation 
becomes more robust.

@@

\pagebreak
\begin{appendices}
    Please refer to \url{https://github.com/QuRyu/CDOT/tree/main/Extensions} for code.
\end{appendices}
